MultiDataGrowthAssessPico

### 2024-01-09 Code/Merge_MCGrowthData.Rmd
Added replicate mean growth estimates and converted growth estimates from per hour to per day

```{r combine unnested fits for PICO Shiny App}

@@

@@

saveRDS(object = LongerFitsData, file = file.path(DataOut, paste(Project, "LongerFitsData.Rds",  sep = "_")), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)

@@

MCGrowthFits %>%
   filter(Strain == "SS120") %>%
  ggplot() +
  geom_point(aes(x = Par_ue, y = deltaOD_Lmu_corr, colour = as.factor(WL)), size = 3, alpha = 0.5) +
 geom_line(aes(x = Par_ue, y = deltaOD_Lmu_corr, colour = as.factor(WL)), linewidth = 0.1, alpha = 0.4) +
   labs(subtitle = "Strain, [Oxygen], Photoperiod, Actinic PAR (nm)", y = "deltaOD [~Chl] " ~ "Logistic Growth Rate" ~ "("~h^-1~")" , x = "Growth Light (µmol photons" ~m^-2 ~s^-1~")") +
 geom_text(aes(x = Par_ue, y = deltaOD_Lmu_corr, label= Run), alpha = 0.5 ,hjust = 0.5, vjust=-0.5) +
  geom_errorbar(aes(x = Par_ue, ymin = (deltaOD_Lmu_corr - deltaOD_Lmu_se), ymax = (deltaOD_Lmu_corr + deltaOD_Lmu_se)), size = 0.3, color = 'black', data = . %>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
  scale_x_continuous(breaks=seq(0, 200, by = 50)) +
  coord_cartesian(xlim = c (0, 200)) +
  #   scale_y_continuous(breaks=seq(-0.03, 0.07, by = 0.01)) +
  # coord_cartesian(ylim = c (-0.03, 0.07)) +
  scale_colour_manual(values = MCMIXColours) +
  ggh4x::facet_nested(cols = vars(Strain, O2_uM, Photoperiod), rows = vars(WL), 
                    labeller = labeller(WL = label_both, O2_uM = label_both, Strain = label_both, Photoperiod = label_value)) +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")

MCGrowthFits %>%
   filter(Strain == "MIT9313",
          deltaOD_Lmu_corr == 0 |
          deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
  ggplot() +
  geom_point(aes(x = Par_ue, y = deltaOD_Lmu_corr, colour = as.factor(WL)), size = 3, alpha = 0.4) +
 geom_line(aes(x = Par_ue, y = deltaOD_Lmu_corr, colour = as.factor(WL)), linewidth = 0.1, alpha = 0.4) +
 labs(subtitle = "Strain, [Oxygen],Photoperiod, Actinic PAR (nm) - Of cultures that grew, outliers filtered by standard error > 20% of growth rate.", y = "deltaOD [~Chl] " ~ "Logistic Growth Rate" ~ "("~h^-1~")" , x = "Growth Light (µmol photons" ~m^-2 ~s^-1~")") +
   geom_text(aes(x = Par_ue, y = deltaOD_Lmu_corr, label= Run), alpha = 0.5,hjust = 0.5, vjust=-0.5) +
  # geom_jitter(aes(x = Par_ue, y = deltaOD_Lmu_corr, colour = as.factor(WL)), size = 6) +
  geom_errorbar(aes(x = Par_ue, ymin = deltaOD_Lmu_corr - deltaOD_Lmu_se, ymax = deltaOD_Lmu_corr + deltaOD_Lmu_se), size = 0.3, color = 'black', data = . %>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
  scale_x_continuous(breaks=seq(0, 200, by = 50)) +
  coord_cartesian(xlim = c (0, 200)) +
  #   scale_y_continuous(breaks=seq(0, 0.07, by = 0.01)) +
  # coord_cartesian(ylim = c (0, 0.07)) +
  scale_colour_manual(values = MCMIXColours) +
  ggh4x::facet_nested(cols = vars(Strain, O2_uM, Photoperiod), rows = vars(WL), 
                    labeller = labeller(WL = label_both, O2_uM = label_both, Strain = label_both, Photoperiod = label_value)) +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")

 MCGrowthFits %>%
   filter(Strain == "MED4",
          deltaOD_Lmu_corr == 0 |
          deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
  ggplot() +
  geom_point(aes(x = Par_ue, y = deltaOD_Lmu_corr, colour = as.factor(WL)), size = 3, alpha = 0.4) +
 geom_line(aes(x = Par_ue, y = deltaOD_Lmu_corr, colour = as.factor(WL)), linewidth = 0.1, alpha = 0.4) +
   labs(subtitle = "Strain, [Oxygen],Photoperiod, Actinic PAR (nm) - Of cultures that grew, outliers filtered by standard error > 20% of growth rate.", y = "deltaOD [~Chl] " ~ "Logistic Growth Rate" ~ "("~h^-1~")" , x = "Growth Light (µmol photons" ~m^-2 ~s^-1~")") +
 geom_text(aes(x = Par_ue, y = deltaOD_Lmu_corr, label= Run), alpha = 0.5,hjust = 0.5, vjust=-0.5) +
  geom_errorbar(aes(x = Par_ue, ymin = deltaOD_Lmu_corr - deltaOD_Lmu_se, ymax = deltaOD_Lmu_corr + deltaOD_Lmu_se), size = 0.3, color = 'black', data = . %>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
  scale_x_continuous(breaks=seq(0, 200, by = 50)) +
  coord_cartesian(xlim = c (0, 200)) +
  #   scale_y_continuous(breaks=seq(0, 0.115, by = 0.01)) +
  # coord_cartesian(ylim = c (0, 0.115)) +
  scale_colour_manual(values = MCMIXColours) +
 ggh4x::facet_nested(cols = vars(Strain, O2_uM, Photoperiod), rows = vars(WL), 
                    labeller = labeller(WL = label_both, O2_uM = label_both, Strain = label_both, Photoperiod = label_value)) +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")

 MCGrowthFits %>%
   filter(Strain == "MIT9313" |
         Strain == "SS120" |
         Strain == "MED4",
          deltaOD_Lmu_corr == 0 |
          deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
  ggplot() +
  geom_point(aes(x = Par_ue, y = deltaOD_Lmu_corr, colour = as.factor(WL)), size = 3, alpha = 0.5) +
  geom_line(aes(x = Par_ue, y = deltaOD_Lmu_corr, colour = as.factor(WL)), linewidth = 0.1, alpha = 0.4) +
labs(subtitle = "Strain, [Oxygen], Photoperiod, Actinic PAR (nm)", y = "deltaOD [~Chl] " ~ "Logistic Growth Rate" ~ "("~h^-1~")" , x = "Growth Light (µmol photons" ~m^-2 ~s^-1~")") +
 geom_text(aes(x = Par_ue, y = deltaOD_Lmu_corr, label= Run),alpha = 0.5 ,hjust = 0.5, vjust=-0.5) +
  geom_errorbar(aes(x = Par_ue, ymin = deltaOD_Lmu_corr - deltaOD_Lmu_se, ymax = deltaOD_Lmu_corr + deltaOD_Lmu_se), size = 0.3, color = 'black', data = . %>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
  scale_x_continuous(breaks=seq(0, 200, by = 50)) +
  coord_cartesian(xlim = c (0, 200)) +
 #   scale_y_continuous(breaks=seq(-0.03, 0.07, by = 0.01)) +
  # coord_cartesian(ylim = c (-0.03, 0.07)) +
  scale_colour_manual(values = MCMIXColours) +
  ggh4x::facet_nested(cols = vars(Strain, O2_uM, Photoperiod), rows = vars(WL), 
                    labeller = labeller(WL = label_both, O2_uM = label_both, Strain = label_both, Photoperiod = label_value)) +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")

>>>>

```{r combine unnested fits}

@@

# Add mean growth estimates for conditions that were replicated. 
```{r add mean growth estimates}
MCGrowthFits <- MCGrowthFits %>% 
   group_by(Strain, WL,  Par_ue, Photoperiod, O2_uM) %>% 
  mutate(ReplicateMean_deltaOD_Lmu_corr = mean(deltaOD_Lmu_corr),
         ReplicateSD_deltaOD_Lmu_corr = case_when(ReplicateMean_deltaOD_Lmu_corr > 0 ~ sd(deltaOD_Lmu_corr),
                                                  ReplicateMean_deltaOD_Lmu_corr <= 0 ~ 0), 
         ReplicateSE_deltaOD_Lmu_corr = ReplicateSD_deltaOD_Lmu_corr/n()^(1/2),
         ReplicateMean_deltaOD_Lmu_corr_day = ReplicateMean_deltaOD_Lmu_corr * 24,
         ReplicateSE_deltaOD_Lmu_corr_day = ReplicateSE_deltaOD_Lmu_corr *24) %>% 
  ungroup() %>% 
  glimpse()

@@

saveRDS(object = LongerFitsData, file = file.path(DataOut, paste(Project, "LongerGrowthFitsData.Rds",  sep = "_")), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)

@@

MCGrowthFits %>%
   filter(Strain == "SS120") %>%
  ggplot() +
  geom_point(aes(x = Par_ue, y = ReplicateMean_deltaOD_Lmu_corr, colour = as.factor(WL)), size = 3, alpha = 0.5) +
 geom_line(aes(x = Par_ue, y = ReplicateMean_deltaOD_Lmu_corr, colour = as.factor(WL)), linewidth = 0.1, alpha = 0.4) +
   labs(subtitle = "Strain, [Oxygen], Photoperiod, Actinic PAR (nm)", y = "deltaOD [~Chl] " ~ "Logistic Growth Rate" ~ "("~h^-1~")" , x = "Growth Light (µmol photons" ~m^-2 ~s^-1~")") +
 geom_text(aes(x = Par_ue, y = ReplicateMean_deltaOD_Lmu_corr, label= Run), alpha = 0.5 ,hjust = 0.5, vjust=-0.5) +
  geom_errorbar(aes(x = Par_ue, ymin = (ReplicateMean_deltaOD_Lmu_corr - deltaOD_Lmu_se), ymax = (ReplicateMean_deltaOD_Lmu_corr + deltaOD_Lmu_se)), size = 0.3, color = 'black', data = . %>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
  scale_x_continuous(breaks=seq(0, 200, by = 50)) +
  coord_cartesian(xlim = c (0, 200)) +
  #   scale_y_continuous(breaks=seq(-0.03, 0.07, by = 0.01)) +
  # coord_cartesian(ylim = c (-0.03, 0.07)) +
  scale_colour_manual(values = MCMIXColours) +
  ggh4x::facet_nested(cols = vars(Strain, O2_uM, Photoperiod), rows = vars(WL), 
                    labeller = labeller(WL = label_both, O2_uM = label_both, Strain = label_both, Photoperiod = label_value)) +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")

MCGrowthFits %>%
   filter(Strain == "MIT9313",
          ReplicateMean_deltaOD_Lmu_corr == 0 |
          ReplicateMean_deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
  ggplot() +
  geom_point(aes(x = Par_ue, y = ReplicateMean_deltaOD_Lmu_corr, colour = as.factor(WL)), size = 3, alpha = 0.4) +
 geom_line(aes(x = Par_ue, y = ReplicateMean_deltaOD_Lmu_corr, colour = as.factor(WL)), linewidth = 0.1, alpha = 0.4) +
 labs(subtitle = "Strain, [Oxygen],Photoperiod, Actinic PAR (nm) - Of cultures that grew, outliers filtered by standard error > 20% of growth rate.", y = "deltaOD [~Chl] " ~ "Logistic Growth Rate" ~ "("~h^-1~")" , x = "Growth Light (µmol photons" ~m^-2 ~s^-1~")") +
   geom_text(aes(x = Par_ue, y = ReplicateMean_deltaOD_Lmu_corr, label= Run), alpha = 0.5,hjust = 0.5, vjust=-0.5) +
  # geom_jitter(aes(x = Par_ue, y = ReplicateMean_deltaOD_Lmu_corr, colour = as.factor(WL)), size = 6) +
  geom_errorbar(aes(x = Par_ue, ymin = ReplicateMean_deltaOD_Lmu_corr - deltaOD_Lmu_se, ymax = ReplicateMean_deltaOD_Lmu_corr + deltaOD_Lmu_se), size = 0.3, color = 'black', data = . %>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
  scale_x_continuous(breaks=seq(0, 200, by = 50)) +
  coord_cartesian(xlim = c (0, 200)) +
  #   scale_y_continuous(breaks=seq(0, 0.07, by = 0.01)) +
  # coord_cartesian(ylim = c (0, 0.07)) +
  scale_colour_manual(values = MCMIXColours) +
  ggh4x::facet_nested(cols = vars(Strain, O2_uM, Photoperiod), rows = vars(WL), 
                    labeller = labeller(WL = label_both, O2_uM = label_both, Strain = label_both, Photoperiod = label_value)) +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")

 MCGrowthFits %>%
   filter(Strain == "MED4",
          ReplicateMean_deltaOD_Lmu_corr == 0 |
          ReplicateMean_deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
  ggplot() +
  geom_point(aes(x = Par_ue, y = ReplicateMean_deltaOD_Lmu_corr, colour = as.factor(WL)), size = 3, alpha = 0.4) +
 geom_line(aes(x = Par_ue, y = ReplicateMean_deltaOD_Lmu_corr, colour = as.factor(WL)), linewidth = 0.1, alpha = 0.4) +
   labs(subtitle = "Strain, [Oxygen],Photoperiod, Actinic PAR (nm) - Of cultures that grew, outliers filtered by standard error > 20% of growth rate.", y = "deltaOD [~Chl] " ~ "Logistic Growth Rate" ~ "("~h^-1~")" , x = "Growth Light (µmol photons" ~m^-2 ~s^-1~")") +
 geom_text(aes(x = Par_ue, y = ReplicateMean_deltaOD_Lmu_corr, label= Run), alpha = 0.5,hjust = 0.5, vjust=-0.5) +
  geom_errorbar(aes(x = Par_ue, ymin = ReplicateMean_deltaOD_Lmu_corr - deltaOD_Lmu_se, ymax = ReplicateMean_deltaOD_Lmu_corr + deltaOD_Lmu_se), size = 0.3, color = 'black', data = . %>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
  scale_x_continuous(breaks=seq(0, 200, by = 50)) +
  coord_cartesian(xlim = c (0, 200)) +
  #   scale_y_continuous(breaks=seq(0, 0.115, by = 0.01)) +
  # coord_cartesian(ylim = c (0, 0.115)) +
  scale_colour_manual(values = MCMIXColours) +
 ggh4x::facet_nested(cols = vars(Strain, O2_uM, Photoperiod), rows = vars(WL), 
                    labeller = labeller(WL = label_both, O2_uM = label_both, Strain = label_both, Photoperiod = label_value)) +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")

 MCGrowthFits %>%
   filter(Strain == "MIT9313" |
         Strain == "SS120" |
         Strain == "MED4",
          ReplicateMean_deltaOD_Lmu_corr == 0 |
          ReplicateMean_deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
  ggplot() +
  geom_point(aes(x = Par_ue, y = ReplicateMean_deltaOD_Lmu_corr, colour = as.factor(WL)), size = 3, alpha = 0.5) +
  geom_line(aes(x = Par_ue, y = ReplicateMean_deltaOD_Lmu_corr, colour = as.factor(WL)), linewidth = 0.1, alpha = 0.4) +
labs(subtitle = "Strain, [Oxygen], Photoperiod, Actinic PAR (nm)", y = "deltaOD [~Chl] " ~ "Logistic Growth Rate" ~ "("~h^-1~")" , x = "Growth Light (µmol photons" ~m^-2 ~s^-1~")") +
 geom_text(aes(x = Par_ue, y = ReplicateMean_deltaOD_Lmu_corr, label= Run),alpha = 0.5 ,hjust = 0.5, vjust=-0.5) +
  geom_errorbar(aes(x = Par_ue, ymin = ReplicateMean_deltaOD_Lmu_corr - deltaOD_Lmu_se, ymax = ReplicateMean_deltaOD_Lmu_corr + deltaOD_Lmu_se), size = 0.3, color = 'black', data = . %>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
  scale_x_continuous(breaks=seq(0, 200, by = 50)) +
  coord_cartesian(xlim = c (0, 200)) +
 #   scale_y_continuous(breaks=seq(-0.03, 0.07, by = 0.01)) +
  # coord_cartesian(ylim = c (-0.03, 0.07)) +
  scale_colour_manual(values = MCMIXColours) +
  ggh4x::facet_nested(cols = vars(Strain, O2_uM, Photoperiod), rows = vars(WL), 
                    labeller = labeller(WL = label_both, O2_uM = label_both, Strain = label_both, Photoperiod = label_value)) +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")
